\documentclass{article}


\providecommand\ttrotatebold{5}
\providecommand\ttrotatenormal{5}


\usepackage[margin = 1in, bottom = .6in]{geometry}
\usepackage{typewriter}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage[bottom]{footmisc}


\newcommand{\davidLink}[2]{\href{#1}{#2}\footnote{\href{#1}{#1}}}


\title{Curriculum Vitae}
\author{David Álvarez Rosa}
\date{\today}


\begin{document}
\pagecolor{gray!6}
\pagestyle{empty}
\maketitle
\thispagestyle{empty}


\section*{Personal information}

\begin{itemize}
  \item Full name: David Álvarez Rosa.
  \item Place and date of birth: Pamplona (Navarra), 10th October 1998.
  \item Mobile Phone: 647 133 930.
  \item Email: \href{mailto:david@alvarezrosa.com}{david@alvarezrosa.com}
\end{itemize}


\section*{Education}

\begin{itemize}
  \item Current
  \begin{itemize}
    \item Degree in Industrial Engineering. 3rd year.
    \href{https://etseib.upc.edu}{ETSEIB} - \href{https://upc.edu}{UPC}.
    \item Degree in Mathematics. 3rd year. \href{https://fme.upc.edu}{FME} -
    \href{https://upc.edu}{UPC}.
  \end{itemize}
  \item June 2017
  \begin{itemize}
    \item Baccalaureate in Science and Technology. Final grade: 9,47/10, getting
    12,757/14 in the exams of access for university (Selectividad).
  \end{itemize}
\end{itemize}


\section*{Languages}

\begin{itemize}
  \item Spanish: mother tongue.
  \item English: C1 level in August 2017.
  \item Catalan: intermediate level.
\end{itemize}


\section*{Technical skills}

\begin{itemize}
  \item Programming languages: good knowledge of C++, Python and Octave. Notions of
  \href{https://en.wikipedia.org/wiki/AMPL}{AMPL} and Bash.
  \item Web development: experience with HTML, CSS and Javascript. Knowledge of
  PHP as a backend language.
  \item Other markup languages: \textsf{\LaTeX} (including
  \href{https://en.wikipedia.org/wiki/Beamer_(LaTeX)}{Beamer}).
  \item Version control: Git.
  \item Linux systems: Arch (current distro), Debian (personal server) and
  (K)ubuntu (in the past).
\end{itemize}


\section*{Relevant courses}

\begin{itemize}
  \item \davidLink{https://sites.google.com/view/dlcfis2019/home}{Introduction to
    Machine Learning/Deep Learning}, CFIS, 20 hours (January 2019,
  Barcelona).
\end{itemize}


\section*{Related projects}

\begin{itemize}
  \item Creation of a study schedule adapted to students through data
  analysis. Developed in group as part of a degree
  \href{https://www.upc.edu/grau/guiadocent/pdf/ing/240044/project-i.pdf}{course}
  in Industrial Engineering.
  \item Mail Server: configuration of modern, secure personal email server based
  on libre software (Postfix, Dovecot, ...) supporting opportunistic TLS and
  IMAP access.
  \item Creation of a \davidLink{https://alvarezrosa.com/proyecto/}{virtual
    animation} of a robotic arm intelligently playing the game of
  Tic-Tac-Toe. Work done in pairs in a
  \href{https://www.upc.edu/grau/guiadocent/pdf/ing/240044/project-ii.pdf}{subject}
  of the degree in Industrial Engineering.
\end{itemize}


\section*{Others}

\begin{itemize}
  \item Second position in the local phase of the Spanish Mathematical Olympiad
  (Navarra, 2016).
  \item Local winner of the Spanish Physics Olympiad (Navarra, 2016).
  \item Silver medal in the Spanish Physics Olympiad (Sevilla, 2016).
  \item Spanish driver's license.
\end{itemize}

\end{document}
