% -*- TeX-master: "../CV - David Álvarez Rosa.tex" -*-

\cvsection{Inspiration}{\faQuoteRight}

\begin{quote}
  ``The science of today is the technology of tomorrow.''
\end{quote}

\cvsection{Skills}{\faRocket}

Accustomed to working in a team, motivated and detailed in projects.%
\divider{}

\textbf{Programming languages.}\\[.5ex]
Solid knowledge of:\\[-2ex]
\begin{center}
  \cvtag{C++}
  \cvtag{Python}
  \cvtag{Octave/Matlab}
\end{center}

Worked with: \quad
\cvtag{Bash}
\cvtag{\href{https://en.wikipedia.org/wiki/R_(programming_language)}{R}}
\cvtag{\href{https://www.ros.org/}{ROS}}
\vspace{.75ex}
\divider{}


Experience in \textbf{web development}:
\vspace{-.05cm}
\begin{center}
  \cvtag{HTML}
  \cvtag{CSS}
  \cvtag{JavaScript}
  \cvtag{PHP}
\end{center}
\divider[empty]{}

Others:
\cvtag{Linux}
\cvtag{Git}
\cvtag{PyTorch}
\cvtag{\LaTeX}

\vspace{-8pt}%
\scalebox{0.00000000001}{%
  \color{white}
  % Sorry, but not enough space and ATS, you know...
  More skills: Machine Learning, Computer Vision, Deep Learning, AMPL, Neural
  Network, Natural Language Processing, Multimodal Learning.%
}


\medskip
\cvsection{Languages}{\faLanguage}

\cvskill{Spanish}{5}
\smallskip
Mother tongue.
\divider{}

\cvskill{English}{4.55}
\smallskip
C1 level accreditation (August 2017).
\divider{}

\cvskill{Catalan}{3.55}
\smallskip
Very good understanding of the language. Intermediate level in oral and written
expression.


\medskip
\cvsection{Awards}{\faTrophy}


\cvachievement{\faTrophy}
{\href{https://rsef.es/olimpiada-espanola-de-fisica}
  {Spanish Physics Olympiad \smallskip}}
{\small\makebox[.5\linewidth][l]{\faCalendar\hspace{0.5em}April 2016}%
  \small\makebox[0.5\linewidth][l]{\faMapMarker\hspace{0.5em}Seville, Andalusia}}
Silver medal in the national phase.

\divider

\cvachievement{\faTrophy}
{\href{https://rsef.es/olimpiada-espanola-de-fisica}
  {Spanish Physics Olympiad \smallskip}}
{\small \makebox[.5\linewidth][l]{\faCalendar\hspace{0.5em}March 2016}%
  \small\makebox[0.5\linewidth][l]{\faMapMarker\hspace{0.5em}Pamplona, Navarre}}
Winner of the local phase.

\divider

\cvachievement{\faTrophy}
{\href{http://www.olimpiadamatematica.es/platea.pntic.mec.es/_csanchez/olimmain.html}
  {Spanish Mathematical Olympiad \smallskip}}
{\small\makebox[.5\linewidth][l]{\faCalendar\hspace{0.5em}January 2016}%
  \small\makebox[0.5\linewidth][l]{\faMapMarker\hspace{0.5em}Pamplona, Navarre}}
Second position in the local phase.
